 

### 2023-04-26 markdown/methods.Rmd
flowchart updated

```{r data_processing_pipeline_flowchart, echo=FALSE, fig.height=10}
library(Gmisc, quietly = TRUE)
library(glue)
library(htmlTable)
library(grid)
library(magrittr)

@@

quality_control_1 <- boxGrob({glue("quality control 1",
                          .sep = "\n")})
qc1_content <- boxGrob("filter out pool samples\n
                             replace zeros with NA\n
                             filter out contaminants\n
                             filter by q-value cutoff\n",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="left"
                       )

@@

quality_control_2 <- boxGrob({glue("quality control 2",
                          .sep = "\n")})
qc2_content <- boxGrob("filter by reporter ion intensity cutoff\n
                             filter by pepitde covariance to razor protein\n
                             remove peptides by missing rate\n",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="left"
                       )

@@

transform_data <- boxGrob({glue("transform data",
                          .sep = "\n")})
transform_opts <- boxGrob("options:\n
                                log2\n
                                log10\n
                                sqrt\n
                                quadratic\n
                                BoxCox\n
                                None",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="left"
                       )

normalize_data <- boxGrob({glue("normalize data",
                          .sep = "\n")})
normalize_opts <- boxGrob("options:\n
                                SCoPE2\n
                                CONSTANd\n
                                None",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="left"
                       )

missing_value_handling <- boxGrob({glue("missing value handling",
                          .sep = "\n")})
missing_value_opts <- boxGrob("options:\n
                                    KNN\n
                                    drop rows\n
                                    replace with mean\n
                                    replace with median\n
                                    replace with 0",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="left"
                       )

batch_correction <- boxGrob({glue("batch correction",
                          .sep = "\n")})
batch_correction_opts <- boxGrob("options:\n
                                       ComBat",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="left"
                       )

dim_red <- boxGrob({glue("dimensionality reduction",
                          .sep = "\n")})
dim_red_actions <- boxGrob("procedures:\n
                                 PCA\n
                                 UMAP",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="left"
                       )

>>>>

```{r data_processing_pipeline_flowchart, echo=FALSE, fig.height=17, fig.width=13}
library(Gmisc, quietly = TRUE)
library(glue)
library(htmlTable)
library(grid)
library(magrittr)

@@

quality_control_1 <- boxGrob({glue("quality control 1",
                          .sep = "\n")})
qc1_content <- boxGrob(
                      "filter out pool samples\nreplace zeros with NA\nfilter out contaminants\nfilter by q-value cutoff",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center",
                       )

@@

quality_control_2 <- boxGrob({glue("quality control 2",
                          .sep = "\n")})
qc2_content <- boxGrob(
                      "filter by reporter ion intensity cutoff\nfilter by pepitde covariance to razor protein\nremove peptides by missing rate",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

@@

transform_data <- boxGrob({glue("transform data",
                          .sep = "\n")})
transform_opts <- boxGrob(
                      "options:\nlog2\nlog10\nsqrt\nquadratic\nBoxCox\nNone",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

normalize_data <- boxGrob({glue("normalize data",
                          .sep = "\n")})
normalize_opts <- boxGrob(
                      "options:\nSCoPE2\nCONSTANd\nNone",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

missing_value_handling <- boxGrob({glue("missing value handling",
                          .sep = "\n")})
missing_value_opts <- boxGrob(
                      "options:\nKNN\ndrop rows\nreplace with mean\nreplace with median\nreplace with 0",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

batch_correction <- boxGrob({glue("batch correction",
                          .sep = "\n")})
batch_correction_opts <- boxGrob(
                      "options:\nComBat",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )

dim_red <- boxGrob({glue("dimensionality reduction",
                          .sep = "\n")})
dim_red_actions <- boxGrob(
                      "procedures:\nPCA\nUMAP",
                       txt_gp = opts_box_setting,
                       box_gp = opts_box_setting,
                       just="center"
                       )
